Ellipsoids (v1.0): 3D Magnetic modelling of ellipsoidal bodies

### 2017-05-31 manuscript/manuscript.tex
Correcao das duas primeiras sugestoes do CLark. Inclui finite na linha 5 e inclui informacoes sobre a existencia de softwares fechados que incluem o modelo elipsoidal na linha 27 da segunda página. Tambem corrigi na pagina 7 na secao 2.4.1 do tensor de depolarizacao que representa um ponto calculado dentro e nao fora do elipsoide.

A considerable amount of literature has been published on the magnetic
modelling of uniformly magnetized ellipsoids since the second half of
the nineteenth century. Ellipsoids have flexibility to represent a wide
range of geometrical forms, are the only known bodies which can be
uniformly magnetized in the presence of a uniform inducing field and
are the only bodies for which the self-demagnetization can be treated
analytically. This property makes ellipsoids particularly useful for
modelling compact orebodies having high susceptibility. In this case,
neglecting the self-demagnetization may strongly mislead the interpretation
of these bodies by using magnetic methods. A number of previous studies
consider that the self-demagnetization can be neglected for the case in
which the geological body has an isotropic susceptibility lower than or
equal to 0.1 SI. This limiting value, however, seems to be determined
empirically and there has been no discussion about how this value was
determined. Besides, the geoscientific community lacks an easy-to-use
tool to simulate the magnetic field produced by uniformly magnetized
ellipsoids. Here, we present an integrated review of the magnetic
modelling of arbitrarily oriented triaxial, prolate and oblate
ellipsoids. Our review includes ellipsoids with both induced and
remanent magnetization, as well as with isotropic or anisotropic
susceptibility. We also propose a
way of determining the isotropic susceptibility above which the
self-demagnetization must be taken into consideration. Tests with
synthetic data validate our approach. Finally, we provide a set
of routines to model the magnetic field produced
by ellipsoids. The routines are written in Python language as
part of the Fatiando a Terra, which is an open-source library
for modelling and inversion in geophysics.

@@

A vast literature about the magnetic
modelling of ellipsoidal bodies was developed in which
are to be found the names of many researchers.
Nevertheless, interest in this subject has not yet died
out, as is evidenced by a list of modern papers in this
field.
Besides, the geoscientific community lacks an easy-to-use
tool to simulate the magnetic field produced by uniformly
magnetized ellipsoids.
Such a tool could prove to be useful either for teaching
and researching geophysics.

@@

Let $\tilde{\mathbf{N}}^{\dagger}$ be the transformed
depolarization tensor calculated for the case in which
$\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation})
represents a point located outside
the ellipsoidal body. In this case,
the elements of $\tilde{\mathbf{N}}^{\dagger}$
are calculated according to Eq. \ref{eq:nij-tilde},
with $\tilde{f}(\tilde{\mathbf{r}})$ given by
$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}).
As we have already pointed out, the
$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}) is a
quadratic function of the spatial coordinates $\tilde{x}$,
$\tilde{y}$ and $\tilde{z}$. Consequently, the
elements $\tilde{n}^{\dagger}_{ij}$, $i = 1, 2, 3$,
$j = 1, 2, 3$, of $\tilde{\mathbf{N}}^{\dagger}$
do not depend on the elements of the transformed position
vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation}).
Besides, the off-diagonal elements are zero and
the diagonal elements are given by \citep{stoner1945}:
\begin{equation}
\tilde{n}^{\dagger}_{ii} = \frac{abc}{2}
\int_{0}^{\infty} \frac{1}{\left( e_{i}^{2}
+ u \right) R(u)} \, du \: , \quad i = 1, 2, 3 \: ,
\label{eq:n-tilde-dagger-ii}
\end{equation}
where $R(u)$ is defined by Eq. \ref{eq:R} and
$e_{1} = a$, $e_{2} = b$, and $e_{3} = c$. These elements
are commonly known as \textit{demagnetizing factors}
and are defined according to the ellipsoid type.
Here, we calculate the demagnetizing factors in the \unit{SI}
system. Consequently, they satisfies the condition
$\tilde{n}^{\dagger}_{11} + \tilde{n}^{\dagger}_{22} +
\tilde{n}^{\dagger}_{33} = 1$, independently of the
ellipsoid type.
It is worth stressing that, according to Eq. \ref{eq:n-tilde-dagger-ii},
the demagnetizing factors $\tilde{n}^{\dagger}_{ii}$ are
constants defined by the ellipsoid semi-axes $a$, $b$, and $c$.

>>>>

A considerable amount of literature has been published on the magnetic
modelling of uniformly magnetized ellipsoids since the second half of
the nineteenth century. Ellipsoids have flexibility to represent a wide
range of geometrical forms, are the only known bodies which can be
uniformly magnetized in the presence of a uniform inducing field and
are the only finite bodies for which the self-demagnetization can be treated
analytically. This property makes ellipsoids particularly useful for
modelling compact orebodies having high susceptibility. In this case,
neglecting the self-demagnetization may strongly mislead the interpretation
of these bodies by using magnetic methods. A number of previous studies
consider that the self-demagnetization can be neglected for the case in
which the geological body has an isotropic susceptibility lower than or
equal to 0.1 SI. This limiting value, however, seems to be determined
empirically and there has been no discussion about how this value was
determined. Besides, the geoscientific community lacks an easy-to-use
tool to simulate the magnetic field produced by uniformly magnetized
ellipsoids. Here, we present an integrated review of the magnetic
modelling of arbitrarily oriented triaxial, prolate and oblate
ellipsoids. Our review includes ellipsoids with both induced and
remanent magnetization, as well as with isotropic or anisotropic
susceptibility. We also propose a
way of determining the isotropic susceptibility above which the
self-demagnetization must be taken into consideration. Tests with
synthetic data validate our approach. Finally, we provide a set
of routines to model the magnetic field produced
by ellipsoids. The routines are written in Python language as
part of the Fatiando a Terra, which is an open-source library
for modelling and inversion in geophysics.

@@

A vast literature about the magnetic
modelling of ellipsoidal bodies was developed in which
are to be found the names of many researchers.
Nevertheless, interest in this subject has not yet died
out, as is evidenced by a list of modern papers in this
field.
Besides, the geoscientific community lacks an free easy-to-use
tool to simulate the magnetic field produced by uniformly
magnetized ellipsoids. There are some commercial software
packages that includes the ellipsoid model, but all very
expensive.
Such a tool could prove to be useful either for teaching
and researching geophysics.

@@

Let $\tilde{\mathbf{N}}^{\dagger}$ be the transformed
depolarization tensor calculated for the case in which
$\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation})
represents a point located inside
the ellipsoidal body. In this case,
the elements of $\tilde{\mathbf{N}}^{\dagger}$
are calculated according to Eq. \ref{eq:nij-tilde},
with $\tilde{f}(\tilde{\mathbf{r}})$ given by
$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}).
As we have already pointed out, the
$\tilde{f}^{\dagger}(\tilde{\mathbf{r}})$ (Eq. \ref{eq:fi-tilde}) is a
quadratic function of the spatial coordinates $\tilde{x}$,
$\tilde{y}$ and $\tilde{z}$. Consequently, the
elements $\tilde{n}^{\dagger}_{ij}$, $i = 1, 2, 3$,
$j = 1, 2, 3$, of $\tilde{\mathbf{N}}^{\dagger}$
do not depend on the elements of the transformed position
vector $\tilde{\mathbf{r}}$ (Eq. \ref{eq:coord_transformation}).
Besides, the off-diagonal elements are zero and
the diagonal elements are given by \citep{stoner1945}:
\begin{equation}
\tilde{n}^{\dagger}_{ii} = \frac{abc}{2}
\int_{0}^{\infty} \frac{1}{\left( e_{i}^{2}
+ u \right) R(u)} \, du \: , \quad i = 1, 2, 3 \: ,
\label{eq:n-tilde-dagger-ii}
\end{equation}
where $R(u)$ is defined by Eq. \ref{eq:R} and
$e_{1} = a$, $e_{2} = b$, and $e_{3} = c$. These elements
are commonly known as \textit{demagnetizing factors}
and are defined according to the ellipsoid type.
Here, we calculate the demagnetizing factors in the \unit{SI}
system. Consequently, they satisfies the condition
$\tilde{n}^{\dagger}_{11} + \tilde{n}^{\dagger}_{22} +
\tilde{n}^{\dagger}_{33} = 1$, independently of the
ellipsoid type.
It is worth stressing that, according to Eq. \ref{eq:n-tilde-dagger-ii},
the demagnetizing factors $\tilde{n}^{\dagger}_{ii}$ are
constants defined by the ellipsoid semi-axes $a$, $b$, and $c$.
